{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-26 thesis/tm.tex
mechanics proofreading - function names, footnote placement, figure optmz, syn hi

\revision{
\begin{figure}[h]
	\begin{center}
		\begin{tabular}{ll}
			1 & \texttt{\flow{if} ((status = \call{\_xbegin}()) == \const{\_XBEGIN\_STARTED}) \{} \\
			%2 & \texttt{~~~~x++;} \\
			$2a$ & \texttt{~~~~temp <- x;} \\
			$2b$ & \texttt{~~~~temp <- temp + 1;} \\
			$2c$ & \texttt{~~~~x <- temp;} \\
			3 & \texttt{~~~~\call{\_xend}();} \\
			4 & \texttt{\} \flow{else} \{} \\
			5 & \texttt{~~~~\call{mutex\_lock}(\&m);} \\
			$6a$ & \texttt{~~~~temp <- x;} \\
			$6b$ & \texttt{~~~~temp <- temp + 1;} \\
			$6c$ & \texttt{~~~~x <- temp;} \\
			7 & \texttt{~~~~\call{mutex\_unlock}(\&m);} \\
			8 & \texttt{\}} \\
		\end{tabular}
	\end{center}
	\caption{\Cref{fig:htm-example-reproduced} with non-atomic operations shown as pseudo-assembly.}
	\label{fig:htm-example-assemblified}
\end{figure}

@@

\begin{figure}[t]
	\begin{center}
		\begin{tabular}{ll}
			\hilight{lavender}{\bf Thread 1} &
			\hilight{seafoam}{\bf Thread 2} \\
			\hline
			\texttt{status = \call{\_xbegin}()} & \\
			\texttt{temp <- x;} & \\
			\texttt{temp <- temp + 1;} & \\
			& \texttt{status = \call{\_xbegin}()} \\
			& \texttt{x++;} \\
			& \texttt{\call{\_xend}();} \\
			\texttt{x <- temp;} & \\
			\texttt{\call{\_xend}();} & \\
		\end{tabular}
	\end{center}
	\caption[Impossible hypothetical interleaving within transactions of \Cref{fig:htm-example-assemblified}.]
		{Impossible hypothetical interleaving within transactions of \Cref{fig:htm-example-assemblified}.
		The effects of $\tiat{2a-2b}$ are never globally visible, as its transaction must abort,
		and moreover $\tiat{2c-3}$ will not execute at all.}
	\label{fig:htm-example-interleaving}
\end{figure}
}

@@

\begin{figure}[h]
	\begin{center}
	\begin{tabular}{p{0.47\textwidth}p{0.5\textwidth}}
		\begin{tabular}{l}
			\texttt{\ctype{static int} num\_in\_section = 0;} \\
			\texttt{\flow{for} (\ctype{int} i = \const{0}; i < \const{NITERS}; i++) \{} \\
			\texttt{~~~~\call{rtm\_spinlock\_acquire}(\&lock);} \\
			\texttt{~~~~num\_in\_section++;} \\
			\texttt{~~~~\flow{if} (!\call{\_xtest()})} \\
			\texttt{~~~~~~~~\call{thr\_yield}(\const{-1});} \\
			\texttt{~~~~\flow{assert}{}(num\_in\_section == \const{1}); } \\
			\texttt{~~~~num\_in\_section--;} \\
			\texttt{~~~~\call{rtm\_spinlock\_release}(\&lock);} \\
			\texttt{\}} \\
		\end{tabular}
		&
		\begin{tabular}{ll}
			\texttt{\flow{for} (\ctype{int} i = \const{0}; i < \const{NITERS}; i++) \{} \\
			\texttt{~~~~\call{rtm\_spinlock\_acquire}(\&lock);} \\
			\texttt{~~~~\flow{assert}{}(\call{\_xtest}());} \\
			\texttt{~~~~\call{rtm\_spinlock\_release}(\&lock);} \\
			\texttt{\}} \\
		\end{tabular}
		\\
		\\
		(a) {\tt lock}(), tests mutual exclusion.
		&
		(b) {\tt lock\_fast}(), tests for no spurious aborts.
	\end{tabular}
	\end{center}
	\caption{Abstraction reduction test cases.}
	\label{fig:htm-lock}
\end{figure}

>>>>

\revision{
\begin{figure}[h]
	\begin{center}
		\begin{tabular}{ll}
			1 & \texttt{\flow{if} ((status = \call{\_xbegin}()) == \const{\_XBEGIN\_STARTED}) \{} \\
			%2 & \texttt{~~~~x++;} \\
			$2a$ & \texttt{~~~~temp <- x;} \\
			$2b$ & \texttt{~~~~temp <- temp + \const{1};} \\
			$2c$ & \texttt{~~~~x <- temp;} \\
			3 & \texttt{~~~~\call{\_xend}();} \\
			4 & \texttt{\} \flow{else} \{} \\
			5 & \texttt{~~~~\call{mutex\_lock}(\&m);} \\
			$6a$ & \texttt{~~~~temp <- x;} \\
			$6b$ & \texttt{~~~~temp <- temp + \const{1};} \\
			$6c$ & \texttt{~~~~x <- temp;} \\
			7 & \texttt{~~~~\call{mutex\_unlock}(\&m);} \\
			8 & \texttt{\}} \\
		\end{tabular}
	\end{center}
	\caption{\Cref{fig:htm-example-reproduced} with non-atomic operations shown as pseudo-assembly.}
	\label{fig:htm-example-assemblified}
\end{figure}

@@

\begin{figure}[t]
	\begin{center}
		\begin{tabular}{ll}
			\hilight{lavender}{\bf Thread 1} &
			\hilight{seafoam}{\bf Thread 2} \\
			\hline
			\texttt{status = \call{\_xbegin}()} & \\
			\texttt{temp <- x;} & \\
			\texttt{temp <- temp + \const{1};} & \\
			& \texttt{status = \call{\_xbegin}()} \\
			& \texttt{x++;} \\
			& \texttt{\call{\_xend}();} \\
			\texttt{x <- temp;} & \\
			\texttt{\call{\_xend}();} & \\
		\end{tabular}
	\end{center}
	\caption[Impossible hypothetical interleaving within transactions of \Cref{fig:htm-example-assemblified}.]
		{Impossible hypothetical interleaving within transactions of \Cref{fig:htm-example-assemblified}.
		The effects of $\tiat{2a-2b}$ are never globally visible, as its transaction must abort,
		and moreover $\tiat{2c-3}$ will not execute at all.}
	\label{fig:htm-example-interleaving}
\end{figure}
}

@@

\begin{figure}[h]
	\begin{center}
	\begin{tabular}{p{0.47\textwidth}p{0.5\textwidth}}
		\begin{tabular}{l}
			\texttt{\ctype{static int} num\_in\_section = \const{0};} \\
			\texttt{\flow{for} (\ctype{int} i = \const{0}; i < \const{NITERS}; i++) \{} \\
			\texttt{~~~~\call{rtm\_spinlock\_acquire}(\&lock);} \\
			\texttt{~~~~num\_in\_section++;} \\
			\texttt{~~~~\flow{if} (!\call{\_xtest()})} \\
			\texttt{~~~~~~~~\call{thr\_yield}(\const{-1});} \\
			\texttt{~~~~\flow{assert}{}(num\_in\_section == \const{1}); } \\
			\texttt{~~~~num\_in\_section--;} \\
			\texttt{~~~~\call{rtm\_spinlock\_release}(\&lock);} \\
			\texttt{\}} \\
		\end{tabular}
		&
		\begin{tabular}{ll}
			\texttt{\flow{for} (\ctype{int} i = \const{0}; i < \const{NITERS}; i++) \{} \\
			\texttt{~~~~\call{rtm\_spinlock\_acquire}(\&lock);} \\
			\texttt{~~~~\flow{assert}{}(\call{\_xtest}());} \\
			\texttt{~~~~\call{rtm\_spinlock\_release}(\&lock);} \\
			\texttt{\}} \\
		\end{tabular}
		\\
		\\
		(a) {\tt lock}(), tests mutual exclusion.
		&
		(b) {\tt lock\_fast}(), tests for no spurious aborts.
	\end{tabular}
	\end{center}
	\caption{Abstraction reduction test cases.}
	\label{fig:htm-lock}
\end{figure}
